Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-11-22 latex/paper.tex
ntroduction 把第三段签名讨论MoS2 黑磷。。。的删掉，然后与第二段合并作为一段;Computational details 部分，第一段关于Mod potential 与LDA, GGA的比较论述删掉

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 10:59:16
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

The existing research about the thermaleletric properties of low-dimensional materials focused on the range of  two-dimensional mateirals with interlayer interaction of  Van der Waals(vdW) type and there is no surface reconstruction. There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure. The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce. Recently, it has been found that monolayer and multilayer silicene material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}. The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers. In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicene, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials. The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.

Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases. For example, the single atom layer $MoS_2$ has a suitable band gap which makes its field effect transistor switching ratio as large as $10^8$ \cite{Li_Yu2014}. Black phosphorus (BP) with thicknesses of several atomic layer have extremely high electron / hole mobility ($1000cm^2/Vs$) and leakage current modulation rates ($10^4$ times of graphene) and the field effect transistor of it has great potential in the application of nano electronic devices\cite{RadisavljevicB2011}. Due to the high thermal conductivity and electron mobility of graphene, it has great potential applications in the field of nano circuits\cite{Chen2008,Balandin2008}. In the case of silicene, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}. And it's expected that the complicated surface reconstruction affects thermal transportation quite a lot, especially it's possible to obtain novel structures with ultralow or highly anistropic thermal conducitivity by changing surface recontruction. This could help reveal a general rule between thermal transportation properties and low-dimensional structures and may promote the application of covalente bonded multilayer 2D materials in the thermaleletricity field.

@@

The thermal conductivity of multilayer silicene structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}. In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicene material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants. It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA). However, these first principle methods tend to overestimate the binding energy of materials and underestimate their equilibrium lattice constants. For this reason, the Mod potential is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

@@

By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction. Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2l3 structure) and the anisotropy can be as high as 41.1\%. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. The ultra-low thermal conductivity indicates that the bilayer silicene 2l3 has good thermoelectric properties. In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive. With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased. The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity and NEGF transmission function. This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-22 12:00:25
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of Boltzmann Transportation Equation (BTE), we systematically study the thermal transportation properties of different types of multilayer silicene. It is found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in interlayer direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicene with different reconstruction can reach up to $57.9 W/mK$, and can be as low as $3.31 W/mK$ and the anisotropy can be as high as $41.1\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction decreases significantly, but the thermal conductivity increases a little in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection of surface reconstruction. Phonon lifetime and group velocity play differenct roles in bilayer structures and 3-8 layer structures where the anisotropy of the former is mainly effected by the anisotropy of lifetime but that of the later is the result of anisotropy of group velocity.  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicene, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

The existing research about the thermaleletric properties of low-dimensional materials focused on the range of  two-dimensional mateirals with interlayer interaction of  Van der Waals(vdW) type and there is no surface reconstruction. There have been lots of studies on the electronic and thermal transport properties for this kind of typical layered structure and hetero structures, such as graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, black phosphorus\cite{Zhang2015,Peng2015,Jain2015} two-dimensional layered structure. The existing preparation technology such as mechanical stripping, molecular beam epitaxy has difficult to produce nano layered structure for the material with strong interaction between layers, and the research of this kind of super thin nano materials has been very scarce. Recently, it has been found that monolayer and multilayer silicene material can be grown on some metal substrates by molecular beam epitaxy\cite{Fleurence2012,Meng2013,Vogt2012,DePadova2013,Feng2012}. The progress of these experiments ignited the upsurge the two dimensional nanomaterials with strong interaction between layers. In contrast to vdW, the two layer nano materials, which are represented by multi-layer silicene, exhibit special surface reconstructions which are different from the bulk surface\cite{Fleurence2012,Meng2013,Feng2012,Guo2013} and its physical and chemical properties are also very unique\cite{Guo2013,Guo2015}, indicating that there is new physics in this kind of ultra-thin nano materials. The study of these of covalent type are relatively rare which may provide a possibitity of high effiency thermaleletric 2D mateirials.Previous studies have shown the big difference of electronic properties in low dimensional phases and build phases. In the case of silicene, the surface reconstruction could be a significant factor which determines wheather it's metal or semiconductor \cite{Guo2015Structural}. And it's expected that the complicated surface reconstruction affects thermal transportation quite a lot, especially it's possible to obtain novel structures with ultralow or highly anistropic thermal conducitivity by changing surface recontruction. This could help reveal a general rule between thermal transportation properties and low-dimensional structures and may promote the application of covalente bonded multilayer 2D materials in the thermaleletricity field.

@@

The thermal conductivity of multilayer silicene structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}. In order to well simulate the structures of different phase by BTE as well as saving computing effort, the latest classical Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicene material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicene structures by fitting its bond angle parameter to give correct melting point and elastic constants and is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.

@@

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair. The dots of 2l2a and 2l2z are almost the same so red solid dots are covered. }
\end{figure}

@@

By means of Boltzmann Transporation Equation (BTE) methods, we found that the thermal transport properties of multilayer silicene structures have significant surface effect and size effect in thickness direction. Under the influence of double layer surface reconstruction, the thermal conductivity of the bilayer silicene can reach up to 57.92 W/mK (2l1 structure), and can be as low as 3.31 W/mK (2l3 structure) and the anisotropy can be as high as 41.1\%. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. The ultra-low thermal conductivity indicates that the bilayer silicene 2l3 has good thermoelectric properties. In the 3-8 layer multilayer silicene with the same $2 \times 1$ surface reconstruction the zigzag direction is more heat conducive. With the increase of the number of layers, the thermal conductivity of the zigzag direction decrease, but the thermal conductivity increased a little in the armchair direction, and the anisotropy of thermal conductivity decreased. The anisotropy mainly comes from phonon scattering effect in bilayer structures while the anisotropy mainly comes from localization of ballistic phonons in 3-8 layer multilayer silicene which could be charactered by phonon group velocity. This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nano materials in the future.
